\documentclass[a4paper,twoside,notitlepage,openany]{tufte-book}
\usepackage[utf8]{inputenc}

% for debugging purposes -- displays the margins
\geometry{showframe}

% The following package makes prettier tables. We're all about the
% bling!
\usepackage{booktabs}

% Clickable hyperlinks
\usepackage{hyperref}
\hypersetup{colorlinks}

\renewcommand{\labelitemi}{$-$} % use dash for items

\title{Best Friends}
\author{Alex Schroeder}
% \date{}
\begin{document}

\maketitle% this prints the handout title, author, and date

This is a game about finding strength in numbers: friends, family,
lovers, children. They are all called \textit{friends} in this game.
Everybody else is just \textit{people}.

\section{Character}

This is a role-playing game and part of the deal is playing a person
that makes a certain \textit{first impression} on people, whether you
want to or not.\marginnote[-2em]{If people's first impression of you
  is that you are strong then that does not mean that you are not
  beautiful. It's just that they don't immediately see it.} Roll on
the table of first impressions to see which one it is.

\begin{table}
  \footnotesize%
  \begin{center}
    \begin{tabular}{cl}
      \toprule
      Roll 1d6 & Result \\
      \midrule
      1 & You are strong. \\
      2 & You are beautiful. \\
      3 & You are cute. \\
      4 & You are wily. \\
      5 & You are quick. \\
      6 & You are dangerous. \\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{First Impressions}
  \label{tab:first-impressions}
\end{table}


\section{Willpower}

You \textbf{willpower} is a number that helps you endure, to suffer
pain, roll with the punches, overcome adversity. It's a bit like hit
points in D\&D.

The number of friends by your side determines your will power. Roll
\textbf{1d6 per person} that stands with you. When you gain a new
friend, reroll your willpower and keep it if it is \textit{higher}
than before. When you lose a friend, reroll your willpower and keep it
if it is \textit{lower} than before.

\newpage

\section{Conflict}

When you are \textbf{arguing}, flirting, making speeches, trying to
influence the people around you, roll 1d6 and reduce the other side's
willpower by that number. It's a bit like automatically dealing damage
in D\&D.

If have less friends than your enemies, you're in trouble. You need to
set up situations where you can bring more friends to the party.
Isolate your enemies, divide and conquer. Or take a time out and go
looking for more friends elsewhere: go on an \textit{adventure}.

If the time for words has passed, you can always \textbf{fight}.
Fighting is dangerous. Each side rolls 2d6 and tries to beat the other
side. If you do, you win. You can get a +1 bonus for various things:

\begin{enumerate}
\item when you have superior numbers, whether friends or ordinary
  people supporting you
\item when you are armored and your opponents are not
\item when you manage to poison them before the attack
\item when you use sorcery to cause additional mayhem
\item when you have knights or soldiers on your side and the others do
  not
\end{enumerate}

The difference between the two rolls shows how \textit{violent} the
encounter was. All your friends need to roll for \textbf{survival}
after a fight. If you won, they need to roll 2d6 over the level of
violence to survive. If you lost, they need to roll 1d6 over the level
of violence to survive. There will be random death if you use
violence, but it might be your best bet if you can't talk it through.
If you're in love with a friend, they get a +1 bonus to their roll.

If you lost and \textbf{no friends survived}, you are captured and are
destined for the dungeons. You disappear from the game until you are
rescued.

If you lost but at least one of your friends survived, you made your
\textbf{escape}.

Don't forget to \textbf{readjust your willpower} after a violent
encounter if you lost any friends.

\newpage

\section{New friends}

When you meet people, you can sometimes make new friends. This is
based on a \textbf{reaction roll}. Roll 2d6 and consult the table
below. Apply a +1 bonus if you are interested in romance. Apply a -1
bonus if you ever broke up with them. It's easy to fall in love and
it's hard to mend a broken friendship.

\begin{table}
  \footnotesize%
  \begin{center}
    \begin{tabular}{cp{7cm}}
      \toprule

      2d6 & Result \\

      \midrule

      2 & They hate your guts and will ally against you as soon as
      possible, possibly stab you in the back. \\
      
      3–5 & They're afraid and angry and won't let you near them. You
      need to undo some perceived setback or slight they believe you
      to be responsible for, even if you're completely innocent. \\
      
      6–8 & They won't commit to anything. You need to prove that you
      can be useful to them. Help them achieve a goal of theirs which
      is \textit{not in your best interest} in order to retool with a
      +1 bonus. \\
      
      9–11 & The atmosphere is friendly and they are well disposed
      towards you, but they're not yet allies. Succeed in a venture
      for the common good to reroll with a +1 bonus. \\
      
      12 & You have made a new friend! \\
      
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{Reaction Roll}
  \label{tab:reactions}
\end{table}

\newthought{ When meeting people,} it can be hard to decide what their
disposition is. Roll on the table of initial dispositions to find out.

\begin{table}
  \footnotesize%
  \begin{center}
    \begin{tabular}{cp{7cm}}
      \toprule

      1d8 & Result \\

      \midrule
      
      1 & They are interested in a romantic, monogamous relationship
      \\
      
      2 & They need a friend that's strong: shoulder to cry on, help
      against bullies. \\
      
      3 & They don't mind an occasional dalliance. They like to be
      around beautiful people. \\
      
      4 & They need a friend that appreciates their qualities. This
      means they like it if you're cute. \\
      
      5 & They have powerful enemies and need a friend that's wily.
      Somebody that will help them plot their revenge. \\
      
      6 & They are a bit dull and a bit slow. They'll admire anybody
      that quick and witty. \\
      
      7 & They are always a bit bored. If you have the air of being a
      dangerous person, they'll feel both fear and excitement. \\
      
      8 & They feel like they're lone wolves. They don't trust anyone.
      \\

      \bottomrule
    \end{tabular}
  \end{center}
  \caption{Initial Dispositions}
  \label{tab:dispositions}
\end{table}

\newpage

\section{Generating adventures}

Have a table of \textbf{names} ready. You'll need it.

\newthought{Roll 1d100} and consult the following list of adventure
ideas.

\paragraph{01}
The servants in this castle are being bullied by the cook. He treats
them badly, ridicules them in public and abuses them in private.
Nobody dares to oppose him because the steward likes the food and does
not want to hear about unrest amongst the servants. Five of the
kitchen boys have learned to obey his rules and he uses them to spy on
you, to steal from you, to trip you, push you, beat you.

\paragraph{02}
…

\end{document}

% Local Variables:
% ispell-local-dictionary: "english"
% End:
